A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-01-22 manuscript.Rmd
add references

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: pdf_document
repro:
  packages:
    - usethis
    - repro
    - here
---

@@

We deem each concept necessary to archive longterm reproducibility.
However, the tools you use to archive them are a mere matter of taste and project requirements.
This tutorial will follow the recommendations of @peikertMissing and utilizes Git for version control, RMarkdown for dynamic document creation, Make for dependency tracking and Docker for software management.
Their interplay is shown in Figure \@ref(fig:schematic).
At several points, we suggest other viable alternatives.

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components (in dashed boxes) central to the reproducible workflow: version control (Git), dependency management (Make), containerization (Docker), and dynamic document generation (R Markdown). Git tracks changes to the project over time. Make manages dependencies among the files. Docker provides a container in which the final report is built using dynamic document generation in R Markdown. Reproduced from @peikertMissing  "}
# file gets downloaded in Makefile
knitr::include_graphics("images/nutshell.svg", auto_pdf = TRUE)
```

@@

## Planing

@@

```r
# package::function → use function from package without library(package)
usethis::use_git()
```

@@

And you could commit it in Git:
<!--I am leaning towards doing everything in R, not sure though-->

@@

@@

Simulating data helps prevent unpleasant surprises and lets you double-check that the data you expect to gather and your analysis fit together.

@@

<!-- Should we design a checklist? -->`

@@

>>>>

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: pdf_document
repro:
  packages:
    - usethis
    - repro
    - here
csl: apa7.csl
bibliography: references.bib
---

@@

We deem each concept necessary to archive longterm reproducibility.
However, the tools you use to archive them are a mere matter of taste and project requirements.
This tutorial will follow the recommendations of @Peikert2019 and utilizes Git for version control, RMarkdown for dynamic document creation, Make for dependency tracking and Docker for software management.
Their interplay is shown in Figure \@ref(fig:schematic).
At several points, we suggest other viable alternatives.

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components (in dashed boxes) central to the reproducible workflow: version control (Git), dependency management (Make), containerization (Docker), and dynamic document generation (R Markdown). Git tracks changes to the project over time. Make manages dependencies among the files. Docker provides a container in which the final report is built using dynamic document generation in R Markdown. Reproduced from @Peikert2019.  "}
# file gets downloaded in Makefile
knitr::include_graphics("images/nutshell.svg", auto_pdf = TRUE)
```

@@

# Planing

@@

```r
# `package::function()` → use function from package without `library(package)`
usethis::use_git()
```

@@

And you could commit it in Git:
<!--I am leaning towards doing everything in R, not sure though-->
<!--For Git we maybe should use RStudio's Git pane-->

@@

We recommend to attend an online lecture or workshop to learn the ins and outs of Git.

@@

There are probably few things as frustrating as realizing that the data that you gathered cannot answer the research question you had in mind.
A step to prevent unpleasant surprises is to simulate data.
Simulated data lets you verify that the data you expect to gather and the analysis that you plan fit together.

@@

<!-- Should we design a checklist? -->

@@

# References
